Students' Alcohol Consumption impacts on academic Results on the example of a secondary Scool Maths Class in Portugal

### 2016-10-11 MSproject.Rmd
reference added
intro completion

@@

>>>>

The dataset used for this paper contains information about students in Portugal at the secondary school level. Portugal is among the world's highest alcohol consuming countries worldwide, ranked as the tenth highest alcohol consuming country per capita (Statitsa, 2016). In addition, Portugal is ranked amongst the top five OECD countries with the largest percentage of adults who have not attained secondary education in 2013, with a high percentage of 65% compared to an OECD average of 25%.  This is coupled with the fact that unemployment affected adults without a secondary education more severely than it did those with tertiary education (OECD, 2013).

=======

@@

Keng, S.H. and Huffman, W.E., 2010. Binge drinking and labor market success: a longitudinal study on young people. Journal of Population Economics, 23(1), pp.303-322.

Statista (2016).  Countries with the highest per capita consumption of alcohol in 2015 (in liters of pure alcohol per year).  Available at https://www.statista.com/statistics/280139/countries-with-highest-per-capita-consumption-of-alcohol/ [Accessed 11.10.2016]

=======
>>>>>>> e1d610a7d350a432b8796c89b01b49246056ddb9
